Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-12 paper.tex
Update paper.tex

>>>>

\documentclass{article}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{graphicx}

\geometry{a4paper, margin=1in}

\begin{longtable}{|l|l|l|l|l|}
\hline
\textbf{Factor} & \textbf{H2O} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
\hline
\endfirsthead

\multicolumn{5}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
\hline
\endhead

\hline \multicolumn{5}{|r|}{\textit{Continued on next page}} \\
\hline
\endfoot

\hline
\endlastfoot

\textbf{Ease of Use} & Easy-to-use GUI and API & Python library, requires coding experience & Very user-friendly web interface, detailed API & Simple API & User-friendly API with minimal coding & Python library with fairly intuitive API\\
\hline
\textbf{Supported Algorithms} & Linear, Tree, DNN, Clustering, etc. & Genetic Programming & Linear, Tree, LightGBM, CatBoost, Clustering, etc. (no DNN) & Linear, Tree, Clustering - More limited and lightweight & Linear, LightGBM, Catboost, etc. & Linear, tree, SVM, etc. \\
\hline
\textbf{Feature Engineering} & Basic & Basic & Advanced - includes feature interactions & Limited & Advanced (automatic) & Basic \\
\hline
\textbf{Time Management} & Time Constraints are Settable & Generations and population size & Time constraints are Settable & Optimized for quick results & Settable time constraints & Settable time constraints\\
\textbf{Ensemble Methods} & Yes (stacking + blending) & Yes (stacking) & Yes (stacking + blending) & No & Yes (stacking) & Yes (stacking) \\
\hline
\textbf{Hyperparameter Tuning} & Automated & Genetic algorithm & Automated and customizable & Automated and efficient tuning & Automated & Automated \\
\hline
\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. & Basic (feature importance) \\
\hline
\hline
\textbf{Scalability} & Good (distributed computing) & Limited & Good & Good (resource-efficient) & Good (distributing computing) & Moderate \\
\hline
\textbf{Customization} & High & Moderate & High & Low-Moderate & Moderate & Moderate \\
\hline

\end{longtable}
